???A quantitative framework for investigating the reliability of network construction

### 2017-09-28 manuscript/CI_interactions.tex
finished my first read-through, updated list of completed figures

  It is fairly straigthforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance (Poisot et al. 2015). Several of these metrics derive directly from quantitative indices of network structure. It is not as easy however to understand how the uncertainty in these estimates do influence network metrics. There are multiple non-linearities in the computation of these metrics and that, because of Jensen's inequality (the principle stating that the average of non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty could bias the average estimate of the metric and influence its variance as well. For instance, among all of the pairs of species for which only few co-occurrences are observed, many of them are truly interacting. If we consider all of these as having no links, then correcting for these false absence would inflate the number of links and therefore influence metrics such as connectance, nestedness and degree distribution. Computing network properties from probabilistic networks is one thing, but then computing them with uncertainties in these probabilities is another problem, far more challenging. Unfortunately, for now we could only rely on computer simulations to get an answer to this problem. In the following section, we will provide an example with the Salix dataset and show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics. We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed fixed entities.

@@

      \emph{Salix}-galler-parasitoid meta-network, here focusing on the smaller \emph{Salix}-galler network. The meta-network consists of interactions between 52? \emph{Salix} species and 222 species of gall-forming insects, sampled from 374 locations in Europe ranging from Sicily to the Arctic. In total, 4295 unique interactions were observed. Each of the 374 locations can be considered as a network in its own right, but here we consider each network as an independent sample from which to build the meta-network.

@@

      In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand. To that end, we use data from another well-described \emph{Salix} galler-parasitoid system~\citep{Barbour2016,Barbour2016Dryad}. Note that this study used several genotypes of \emph{S. hookeriana} rather than different \emph{Salix} species. We estimated frequencies of  \emph{S. hookeriana} genotype-galler and galler-parasitoid interactions [[host-parasitoid still to-do]] based on the normalized degree of each species in each network component (see \emph{Appendix S1} for details and code).

@@

    Rather than calculating confidence intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler system is below 0.5, 0.1, or 0.01, we would need 6, 54, and 114 observed co-occurrances with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}). Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many "non-interacting" pairs of species. Even in the \emph{Salix}-galler dataset, [[how many pairs of species co-occur in \textgreater6,54,114 sites?]].  Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling.

@@

>>>>

    It is fairly straigthforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}. Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$; the remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one. It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics. Computation of these metrics involves non-linear functions and therefore, because of Jensen's inequality (which states that the average of non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty in $\lambda$s could bias both the mean and variance of a network metric. For instance, assume that among all pairs of species with few observed co-occurances there are many pairs which truly interact.    If we begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution. While we can, as described above, calculate these network metrics using fixed estimates for $\lambda$ no analytical solution currently exists for uncertain $\lambda$. Instead we must rely on computer simulations. In the following section, we will provide an example with the Salix dataset and show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics. We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed fixed entities.

@@

      [[Kate, can you expand this?]]
      \emph{Salix}-galler-parasitoid meta-network, here focusing on the smaller \emph{Salix}-galler network. The meta-network consists of interactions between 52? \emph{Salix} species and 222 species of gall-forming insects, sampled from 374 locations in Europe ranging from Sicily to the Arctic. In total, 4295 unique interactions were observed. Each of the 374 locations can be considered as a network in its own right, but here we consider each network as an independent sample from which to build the meta-network.

@@

      [[Do we want the host-parasitoid site too, or is the plant-galler enough? This is feeling long already.]]
      In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand. To that end, we use data from another well-described \emph{Salix} galler-parasitoid system~\citep{Barbour2016,Barbour2016Dryad}. Note that this study used several genotypes of \emph{S. hookeriana} rather than different \emph{Salix} species. We estimated frequencies of  \emph{S. hookeriana} genotype-galler interactions based on the normalized degree of each species in each network component (see \emph{Appendix S1} for details and code).

@@

      Rather than calculating confidence intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler system is below 0.5, 0.1, or 0.01, we would need six, 54, and 114 observed co-occurrances with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}). Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many "non-interacting" pairs of species. Even in the extensively replicated \emph{Salix}-galler dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (173/4992 pairs were observed at least six times, two pairs were observed at least 54 times, and no pair was observed more than 114 times). Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling.

@@

  \subsection*{Scaling up to network metrics}
